Stable Hot Spot Analysis (Draft)

### 2017-06-08 paper-main.tex
Added First Structure

Fig.~\ref{fig:ComparisonMorning} and Fig.~\ref{fig:ComparisonEvening} show
Standard and Focal $G^*$ computations for both morning and eventing datasets
with weight matrix $W$ of size 3, 5, 7, 9, 15 and 31. In this figures, when 
computing Focal
$G^*$, the focal matrix $F$ has a constant size of $61{\times}61$ cells. 
Example weight matrix $W$ and focal matrix $F$ are depicted in 
Fig.~\ref{fig:ExampleMatrices}.

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{Morning}
    \includegraphics[width=\linewidth]{images/hotspot-eval-gstar-1}
    \label{fig:EvalMorning}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{Eveninig}
    \includegraphics[width=\linewidth]{images/hotspot-eval-gstar-2}
    \label{fig:EvalEvening}
  \end{subfigure}
  \caption{Evaluation results - Standard vs Focal $G^*$}
  \label{fig:EvalResults}
\end{figure}

%We used square weight matrices of nrow=ncol= 3, 5, 7, \ldots, 41.
%
%- We experimented with different sizes of matrix $F$.
%- The most stable results were achieved when $all(dim(F) == dim(W))$.

To evaluate the stability of our proposed Focal $G^*$, we compare it to two 
baselines:
\begin{itemize}
  \item Standard $G^*$, which uses the same weight matrix $W$ as our focal 
  version.
  \item Standard $G^*$, which uses square weight matrix with all cells set to 1.
\end{itemize}

The evaluation results are plotted in Fig.~\ref{fig:EvalResults}, each point in
the graph represents the $SoH^\uparrow$ metric (Eq.\ref{eq:SoH-up}) between two
$G^*$ generated using weight matrices of size $i$ and $i+2$. The focal matrix F
has a fixed size of $41{\times}41$

\begin{displaymath}
SoH^\uparrow( G^*(R, W_i, st), G^*(R, W_{i+2}, st) )
\end{displaymath}

\begin{figure}[htp]
  \centering
  \begin{subfigure}{.45\columnwidth}
    \centering
    \caption{Weight matrix $W$}
    \includegraphics[width=9em]{images/hotspot-weight-matrix-1}
  \end{subfigure}
  \begin{subfigure}{.45\columnwidth}
    \centering
    \caption{Focal matrix $F$}
    \includegraphics[width=9em]{images/hotspot-eval-gstar-focus-matrix-1}
  \end{subfigure}
  \caption{Example matrices $W$ and $F$}
  \label{fig:ExampleMatrices}
\end{figure}

>>>>

\section{Results}
\subsection{Heatmap}
\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{FocalRelation}
    \includegraphics[width=\linewidth]{images/FocalRealationUp}
    \label{fig:FocalRelation}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{WeightRealtion}
    \includegraphics[width=\linewidth]{images/WeightRelationUp}
    \label{fig:WeightRealtion}
  \end{subfigure}
  \caption{Heatmap of Relation between size of weight matrix $W$ and focal matrix $F$}
  \label{fig:RealtionUp}
\end{figure}

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{FocalRelation}
    \includegraphics[width=\linewidth]{images/FocalRealationDown}
    \label{fig:FocalRelation}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{WeightRealtion}
    \includegraphics[width=\linewidth]{images/WeightRelationDown}
    \label{fig:WeightRealtion}
  \end{subfigure}
  \caption{Heatmap of Relation between size of weight matrix $W$ and focal matrix $F$}
  \label{fig:RealtionDown}
\end{figure}
\subsection{Clumping}

\subsection{Zoom}

Blueline is Focal $G^*$. Redline is $G^*$

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{Upward}
    \includegraphics[width=\linewidth]{images/SoHZoomUp}
    \label{fig:UpwardZoom}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{Downward}
    \includegraphics[width=\linewidth]{images/SoHZoomDown}
    \label{fig:DownwardZoom}
  \end{subfigure}
  \caption{TODO}
  \label{fig:Zoom}
\end{figure}

\subsection{Blur}

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{Upward}
    \includegraphics[width=\linewidth]{images/SoHUpBlur}
    \label{fig:UpwardBlur}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{Downward}
    \includegraphics[width=\linewidth]{images/SoHDownBlur}
    \label{fig:DownwardBlur}
  \end{subfigure}
  \caption{TODO}
  \label{fig:Blur}
\end{figure}
